---
title: "9/25 Lab Meeting"
author: "Tena Dhayalan"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: cosmo
    toc: yes
    toc_float:
      collapsed: true
---
  
```{r,echo=FALSE, message=FALSE}
library(knitr)
require(kableExtra)
library(tidyverse)
options(knitr.table.format = "html")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,    # Show warnings
  message = FALSE,    # Show messages
  error = FALSE       # Show errors
)
```

# Question
How do ocean warming and acidification affect *Silvetia compressa* and *Tegula eiseni* individually and their resulting interaction

# Hypotheses
1. Both species will converge in their response to warming
2. *Tegula* will be more negatively affected by decreasing pH than *Silvetia*

# Experimental Design
- 2 30-day experiments
- 9 pHs (7.2-8.0)
- 2 temps (14^C, 16^C)
- each tank has 3 no predator controls and 3 predator treatments

## Measuring:
- **growth**
- **respiration**
- **calcification**
- predation

# Loading libraries 
```{r}
library(dplyr)
library(broom)
library(purrr)
library(lubridate)
library(tidyverse)
library(nlstools)
library(here)
library(stringr)
library(lmerTest)
library(lme4)
```


# Load datasets 
```{r}
respo <- read_csv(here("Data","PR_2024","Metadata_combined.csv"))
respo <- respo %>%
  filter(Species == "Tegula")
calc <- read_csv(here("Data", "TA", "Calcification_clean.csv"))
maypH <- read_csv(here("Data","pH_temp","ph_temp_may_final.csv"))
aprilpH <- read_csv(here("Data","pH_temp","ph_temp_final.csv"))
aprilTeg <- read_csv(here("Data","growth","tegula_initial_april.csv"))
mayTeg <- read_csv(here("Data","growth","tegula_initial_may.csv"))
Respo.R <- read_csv(here("Data","PR_2024","Respo_final.csv"))
Sample.Info <- read_csv(file = here("Data","PR_2024","Metadata_combined.csv"))
respo_clean <-read.csv(here("Data", "PR_2024","PR_final_normalized_clean.csv"))
respo_dry_clean <- read.csv(here("Data", "PR_2024","PR_final_normalized_dry_clean.csv"))
```

# pH and temperature
Data used for these plots are the daily measurements taken using the Orion and Temperature probe, haven't included Apex or HOBO logging so these are snapshots rather than continuous measurements.

## April
```{r echo=FALSE}
aprilpH$discrete <- cut(aprilpH$expected_temp, breaks = 2, labels = c("Low", "High"))
ggplot(data=aprilpH, aes(x=expected_pH,y=pH, group = interaction(expected_pH,discrete), fill = discrete, color = discrete))+
  geom_boxplot(alpha=0.5, outlier.alpha=0) + 
  scale_y_continuous(breaks = seq(7.0, 8.1, by=0.1), limits=c(7.0,8.1))+
  scale_x_continuous(breaks = seq(7.1, 8.1, by=0.1), limits=c(7.1,8.1))+
  scale_fill_manual(values=c("Low" = "#0072B2", "High" = "tomato"))+
  scale_color_manual(values=c("Low" = "#0072B2", "High" = "tomato"))+
  labs(title = "April pH", x="Expected pH", y= "Measured pH")+
  theme_bw()
aprilpH$discrete <- cut(aprilpH$expected_temp, breaks = 2, labels = c("Low", "High"))
ggplot(data=aprilpH, aes(x=expected_temp,y=TempInSitu, group=expected_temp, fill=discrete))+
  geom_boxplot(alpha=0.5, outlier.alpha=0) + 
  scale_fill_manual(values=c("Low" ="#0072B2", "High"="tomato"))+
  #geom_jitter(width=0.25, pch=21, size=2) +
  labs(title = "April temperature", x="Expected temp", y= "Measured temp")+
  theme_bw()
```

## May
```{r echo=FALSE}
maypH$discrete <- cut(maypH$expected_temp, breaks = 2, labels = c("Low", "High"))
ggplot(data=maypH, aes(x=expected_pH,y=pH, group = interaction(expected_pH,discrete), fill = discrete, color = discrete))+
  geom_boxplot(alpha=0.5, outlier.alpha=0) + 
  scale_y_continuous(breaks = seq(7.0, 8.1, by=0.1), limits=c(7.0,8.1))+
  scale_x_continuous(breaks = seq(7.1, 8.1, by=0.1), limits=c(7.1,8.1))+
  scale_fill_manual(values=c("Low" = "#0072B2", "High" = "tomato"))+
  scale_color_manual(values=c("Low" = "#0072B2", "High" = "tomato"))+
  labs(title = "May pH", x="Expected pH", y= "Measured pH")+
  theme_bw()
maypH$discrete <- cut(maypH$expected_temp, breaks = 2, labels = c("Low", "High"))
ggplot(data=maypH, aes(x=expected_temp,y=TempInSitu, group=expected_temp, fill=discrete))+
  geom_boxplot(alpha=0.5, outlier.alpha=0) + 
  scale_fill_manual(values=c("Low" ="#0072B2", "High"="tomato"))+
  #geom_jitter(width=0.25, pch=21, size=2) +
  labs(title = "May temperature", x="Expected temp", y= "Measured temp")+
  theme_bw()
```

# Growth
Simply calculated as the final weight - initial weight

## Wet weight

### April
```{r}
aprilTeg <- aprilTeg[-16,] #outlier
aprilTeg$wet_weight <- aprilTeg$final_wet_weight - aprilTeg$blotted_wet_weight_g #calculate final - initial
aprilTeg$discrete <- cut(aprilTeg$temp, breaks = 2, labels = c("Low", "High")) #separate temperature treatments
ggplot(data=aprilTeg, aes(x=pH, y=wet_weight, group = interaction(pH,discrete), fill = discrete, color = discrete))+
  geom_boxplot(alpha=0.5, outlier.alpha=0) + 
  scale_x_continuous(breaks = seq(7.1, 8.1, by=0.1), limits=c(7.1,8.1))+
  scale_fill_manual(values=c("Low" = "#0072B2", "High" = "tomato"))+
  scale_color_manual(values=c("Low" = "#0072B2", "High" = "tomato"))+
  labs(x="pH", y= "Change in wet weight (g)")+
  theme_bw()
```

### May
```{r}
mayTeg$wet_weight <- mayTeg$final_wet_weight - mayTeg$blotted_wet_weight_g #calculate final - initial
mayTeg$discrete <- cut(mayTeg$temp, breaks = 2, labels = c("Low", "High")) #separate temperature treatments
ggplot(data=mayTeg, aes(x=pH, y=wet_weight, group = interaction(pH,discrete), fill = discrete, color = discrete))+
  geom_boxplot(alpha=0.5, outlier.alpha=0) + 
  scale_x_continuous(breaks = seq(7.1, 8.1, by=0.1), limits=c(7.1,8.1))+
  scale_fill_manual(values=c("Low" = "#0072B2", "High" = "tomato"))+
  scale_color_manual(values=c("Low" = "#0072B2", "High" = "tomato"))+
  labs(x="pH", y= "Change in wet weight (g)")+
  theme_bw()
```

## Wet weight to dry weight regressions

### April
```{r}
aprilWDReg <- lm(aprilTeg$final_dry_weight~aprilTeg$blotted_wet_weight_g) # regression of wet to dry weight
april_sum <- summary(aprilWDReg) # get model summary
april_r <- april_sum$r.squared
plot(aprilTeg$blotted_wet_weight_g,aprilTeg$final_dry_weight, xlab = "Final wet weight (g)", ylab = "Final dry weight (g)") #plot wet weight x dry weight
abline(aprilWDReg) # add regression line
text(3.3, 0.1, paste("R² =", round(april_r, 2)), col="black", cex=1.2)

```

### May
```{r}
mayWDReg <- lm(mayTeg$final_dry_weight~mayTeg$blotted_wet_weight_g) # regression of wet weight to dry weight
may_sum <- summary(mayWDReg)
may_r <- may_sum$r.squared
plot(mayTeg$blotted_wet_weight_g,mayTeg$final_dry_weight, xlab = "Final wet weight (g)", ylab = "Final dry weight (g)") #plot wet weight x dry weight
abline(mayWDReg) # add regression line
text(2.3, 0.05, paste("R² =", round(may_r, 2)), col="black", cex=1.2)
        
```

## Without shell weight

### April
```{r}
aprilTeg$wet_body <- aprilTeg$blotted_wet_weight_g-aprilTeg$dry_shell
aprilWDReg2 <- lm(aprilTeg$final_dry_weight~aprilTeg$wet_body) # regression of wet to dry weight
april_sum2 <- summary(aprilWDReg2) # get model summary
april_r2 <- april_sum2$r.squared
plot(aprilTeg$wet_body,aprilTeg$final_dry_weight, xlab = "Final wet weight - shell (g)", ylab = "Final dry weight (g)")+ #plot wet weight x dry weight
abline(aprilWDReg2) # add regression line
text(0.65, 0.1, paste("R² =", round(april_r2, 2)), col="black", cex=1.2)

```

### May
```{r}
mayTeg$wet_body <- mayTeg$blotted_wet_weight_g-mayTeg$dry_shell
mayWDReg2 <- lm(mayTeg$final_dry_weight~mayTeg$wet_body) # regression of wet to dry weight
may_sum2 <- summary(mayWDReg2) # get model summary
may_r2 <- may_sum2$r.squared
plot(mayTeg$wet_body,mayTeg$final_dry_weight, xlab = "Final wet weight - shell (g)", ylab = "Final dry weight (g)")+ #plot wet weight x dry weight
abline(mayWDReg2) # add regression line
text(0.2, 0.05, paste("R² =", round(may_r2, 2)), col="black", cex=1.2)

```

# Respiration
```{r}
Respo.R<-Respo.R %>% # Bring in respo data post-thinning
  left_join(Sample.Info) %>% # Join the raw respo calculations with the metadata
  mutate(umol.sec = umol.L.sec*(volume/1000)) %>% #Account for chamber volume to convert from umol L-1 s-1 to umol s-1. This standardizes across water volumes and removes per Liter
  mutate_if(sapply(., is.character), as.factor) %>% #convert cha-=racter columns to factors
  mutate(BLANK = as.factor(BLANK)) #make the blank column a factor

```

### Check blanks
Clearly an outlier, decided to average blanks per pH treatment
```{r}
Respo.R %>% 
  filter(BLANK == "1") %>%
  filter(Species == "Tegula") %>%
  ggplot(aes(x=as.factor(pH_treatment),y=umol.L.sec, group = interaction(pH_treatment, temp_treatment), color=temp_treatment))+
  geom_boxplot()+
  geom_point()

```

## Wet weight
```{r}
respo_clean$temp_treatment <- as.factor(respo_clean$temp_treatment)
respo_clean$experiment <- as.numeric(respo_clean$experiment)
tegrespo <- respo_clean %>%
  filter(Species == "Tegula") ##filter out rockweeds

teganova_reduced <- lm(Respiration ~ poly(pH_treatment,2) * temp_treatment, data=tegrespo)
#plot(teganova) #check assumptions
anova(teganova_reduced)

#with random effect
teganova_full <- lmer(Respiration ~ poly(pH_treatment,2) * temp_treatment + (1|experiment), data=tegrespo)
anova(teganova_full)
anova(teganova_full,teganova_reduced) #full model is better
summary(teganova_full)

#prediction for model
tegrespo <- tegrespo %>%
  mutate(model = predict(teganova_reduced))

```

Respiration increases with temperature

```{r echo=FALSE}
tegrespo %>%
  ggplot(aes(x=as.factor(pH_treatment), y=Respiration, fill=as.factor(temp_treatment)))+
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.8, alpha = 0.3) +
  stat_summary(aes(color = as.factor(temp_treatment)), fun.data = mean_se, fun.args = list(mult = 1), 
               geom = "pointrange", size = 0.5) +
  geom_line(aes(y = model, group = temp_treatment, color = as.factor(temp_treatment))) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y = expression(Respiration~rate~(μmol~O[2]~g^-1~hr^-1)))
```

## Respo vs initial size
```{r echo=FALSE}
tegsizerespo <- Respo.R %>%
  filter(Species == "Tegula") ##filter out rockweeds
tegsizerespo$initial_wet_weight <- as.numeric(tegsizerespo$initial_wet_weight)
tegsizerespo %>%
  ggplot(aes(x=initial_wet_weight, y=umol.L.sec))+
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.8, alpha = 0.3) +
  facet_wrap(~experiment)+
  stat_summary(aes(color = as.factor(temp_treatment)), fun.data = mean_se, fun.args = list(mult = 1), 
               geom = "pointrange", size = 0.5) +
  #geom_line(aes(y = model, group = temp_treatment, color = as.factor(temp_treatment))) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) 
  #labs(x = expression(pH[T]),
   #    color = "Temperature",
    #   fill = "Temperature",
     #  y = expression(Respiration~rate~(μmol~O[2]~g^-1~hr^-1)))
```

## Dry Weight

```{r}
Respo.R_Normalized_Dry <- Respo.R %>%
  group_by(block, pH_treatment, Light_Dark, Species, BLANK)%>% 
  summarise(umol.sec = mean(umol.sec, na.rm=TRUE)) %>%
  filter(BLANK ==1)%>% # only keep the actual blanks
  dplyr::select(block, pH_treatment, Light_Dark, Species, blank.rate = umol.sec) %>% # only keep what we need and rename the blank rate column
  right_join(Respo.R, by = c("block", "pH_treatment", "Light_Dark", "Species")) %>% # join with the respo data %>%
  mutate(umol.sec.corr = umol.sec - blank.rate, # subtract the blank rates from the raw rates
         umol.gram.hr = (umol.sec.corr*3600)/dry_weight)  %>% # convert to umol g hr-1
  filter(BLANK ==0) %>% # remove all the blank data
  dplyr::select(Date, Species, pH_treatment, temp_treatment, Light_Dark, ID, dry_weight, umol.gram.hr) #keep only what we need-

Respo.R_Normalized_Dry<- Respo.R_Normalized_Dry %>%
  dplyr::select(!Date) %>%
  pivot_wider(names_from = Light_Dark, values_from = umol.gram.hr) %>%
  rename(Respiration = Dark)%>% 
         # NetPhoto = Light) %>% # rename the columns
  mutate(Respiration = - Respiration # Make respiration positive
        # GrossPhoto = Respiration + NetPhoto
  )

write_csv(Respo.R_Normalized_Dry,here("Data","PR_2024","PR_final_normalized_dry_clean.csv"))# export all the uptake rates
```


```{r echo=FALSE}
respo_dry_clean$temp_treatment <- as.factor(respo_dry_clean$temp_treatment)
respo_dry_clean$experiment <- as.numeric(respo_dry_clean$experiment)
tegrespodry <- respo_dry_clean %>%
  filter(Species == "Tegula") ##filter out rockweeds

```
## Linear model?

```{r}
  teganovadry_reduced_l <- lm(Respiration ~ pH_treatment * temp_treatment, data=tegrespodry)
 #plot(teganovadry_reduced_l) #check assumptions
  anova(teganovadry_reduced_l)

  #with experiment, random effect loses too much power
  teganovadry_full_l <- lm(Respiration ~ pH_treatment * temp_treatment + experiment, data=tegrespodry)
  anova(teganovadry_full_l)
  anova(teganovadry_full_l,teganovadry_reduced_l) #full model is better

  #prediction for model
  tegrespodry_l <- tegrespodry %>%
  mutate(model = predict(teganovadry_reduced_l))
  
#graph
  tegrespodry_l %>%
  ggplot(aes(x=as.factor(pH_treatment), y=Respiration, fill=as.factor(temp_treatment)))+
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.8, alpha = 0.3) +
  stat_summary(aes(color = as.factor(temp_treatment)), fun.data = mean_se, fun.args = list(mult = 1), 
               geom = "pointrange", size = 0.5) +
  geom_line(aes(y = model, group = temp_treatment, color = as.factor(temp_treatment))) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y = expression(Respiration~rate~(μmol~O[2]~g^-1~hr^-1)))
  
```  

## 2nd Order Polynomial?
```{r}
  teganovadry_reduced_2 <- lm(Respiration ~ poly(pH_treatment,2) * temp_treatment, data=tegrespodry)
  #plot(teganovadry_reduced_2) #check assumptions
  anova(teganovadry_reduced_2)

  #with experiment effect
  teganovadry_full_2 <- lm(Respiration ~ poly(pH_treatment,2) * temp_treatment + experiment, data=tegrespodry)
  anova(teganovadry_full_2)
  anova(teganovadry_full_2,teganovadry_reduced_2) #full model is better

  #prediction for model
  tegrespodry_2 <- tegrespodry %>%
  mutate(model = predict(teganovadry_reduced_2))
  
#graph
  tegrespodry_2 %>%
  ggplot(aes(x=as.factor(pH_treatment), y=Respiration, fill=as.factor(temp_treatment)))+
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.8, alpha = 0.3) +
  stat_summary(aes(color = as.factor(temp_treatment)), fun.data = mean_se, fun.args = list(mult = 1), 
               geom = "pointrange", size = 0.5) +
  geom_line(aes(y = model, group = temp_treatment, color = as.factor(temp_treatment))) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y = expression(Respiration~rate~(μmol~O[2]~g^-1~hr^-1)))
```

## Gaussian model?
```{r}
  teganovadry_reduced_g <- glm(Respiration ~ pH_treatment * temp_treatment, family = gaussian, data=tegrespodry)
  #plot(teganovadry_reduced_g) #check assumptions
  anova(teganovadry_reduced_g)

  #with experiment
  teganovadry_full_g <- glm(Respiration ~ pH_treatment * temp_treatment + experiment, family = "gaussian", data=tegrespodry)
  anova(teganovadry_full_g)
  anova(teganovadry_full_2,teganovadry_reduced_g) #full model is better

  #prediction for model
  tegrespodry_g <- tegrespodry %>%
  mutate(model = predict(teganovadry_reduced_g))
  
#graph
  tegrespodry_g %>%
  ggplot(aes(x=as.factor(pH_treatment), y=Respiration, fill=as.factor(temp_treatment)))+
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.8, alpha = 0.3) +
  stat_summary(aes(color = as.factor(temp_treatment)), fun.data = mean_se, fun.args = list(mult = 1), 
               geom = "pointrange", size = 0.5) +
  geom_line(aes(y = model, group = temp_treatment, color = as.factor(temp_treatment))) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y = expression(Respiration~rate~(μmol~O[2]~g^-1~hr^-1)))


```
### Model comparison
```{r}
AIC(teganovadry_full_l)
AIC(teganovadry_full_2)
AIC(teganovadry_full_g)
```

# Calcification

```{r}
#get initial data
rows.initial <- which(calc$sample_type == "Initial") #tells you all the rows that you have with initial
initial <- calc[rows.initial,]

#take means of initial data
initial_mean <- initial %>%
  group_by(tank) %>%
  summarise(TA_initial = mean(TA))

#bring initials into data frame by tank
calc <- calc %>%
  left_join(initial_mean, by= c("tank"))


#get blank data
rows.blank <- which(calc$sample_type == "Blank") #tells you all the rows that you have with blank
blanks <- calc[rows.blank,]

#figure out delta TA, initial-final

blanks$delta.TA.blank <- blanks$TA_initial - blanks$TA

#add blank column
mean.blanks <- blanks %>% 
  group_by(tank) %>%
  summarise(mean.blanks=mean(delta.TA.blank)) 

calc <- left_join(calc, mean.blanks) #bring in mean blanks to calc.data

#bring in time, mass, volume

time.data <- respo[, c("ID", "tank", "pH_treatment", "temp_treatment", "volume", "wet_weight", "TA.start", "TA.stop", "dry_weight", "dry_shell_weight")] 
calc$tank <- as.character(calc$tank) # convert tank to character to join

full.calc <- left_join(calc, time.data)

##get rid of NAs
clean.full.calc <- full.calc %>%
  filter(!is.na(TA.start))

#adjust the time information and format
clean.full.calc$TA.start <- strptime(as.character(clean.full.calc$TA.start), "%H:%M:%S")
clean.full.calc$TA.stop <- strptime(as.character(clean.full.calc$TA.stop), "%H:%M:%S")
#calculate the NEC rate

clean.full.calc$deltaTA<- (clean.full.calc$TA_initial - clean.full.calc$TA) - clean.full.calc$mean.blanks
clean.full.calc$timediff <- as.numeric((clean.full.calc$TA.stop - clean.full.calc$TA.start)) 

#convert volume from mL to L
clean.full.calc$volume <- clean.full.calc$volume * 0.001

```

## Normalize to dry weight
```{r}
#equation to calculate NEC rates 
clean.full.calc$umol.cm2.hr<-((clean.full.calc$deltaTA/2)*(1.025)*(clean.full.calc$volume))/((clean.full.calc$dry_weight)*(clean.full.calc$timediff))


#write_csv(clean.full.calc, here("Data","TA","NEC.csv"))
```

### Check blanks and initials
```{r}
blanks %>%
  ggplot(aes(x=tank, y=TA))+
  geom_point()+
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"))+
  labs(title="Blanks")

initial %>%
  ggplot(aes(x=tank, y=TA))+
  geom_point()+
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"))+
  labs(title="Initial")
```

### Linear?
```{r}
#Linear ancova
  calclin_reduced <- lm(umol.cm2.hr ~ pH_treatment * temp_treatment, data = clean.full.calc)
  #plot(calcpoly)
  anova(calclin_reduced)

  #with with effect for experiment
  calclin_full <-lm(umol.cm2.hr ~ pH_treatment * temp_treatment + experiment, data = clean.full.calc)
  anova(calclin_full)

  AIC(calclin_full)
  AIC(calclin_reduced) #lower

clean.full.calc <- clean.full.calc %>%
  mutate(model = predict(calclin_reduced)) #model prediction for plot
```

```{r echo=FALSE}
ggplot(data = clean.full.calc, aes(x = pH_treatment, y = umol.cm2.hr, group = interaction(pH_treatment, temp_treatment), fill = as.factor(temp_treatment))) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.8, alpha = 0.3) +
  stat_summary(aes(color = as.factor(temp_treatment)), fun.data = mean_se, fun.args = list(mult = 1), 
               geom = "pointrange", size = 0.5) +
  geom_line(aes(y = model, group = temp_treatment, color = as.factor(temp_treatment))) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
       text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y = expression(Calcification~rate~(μmol~CO[3]~g^-1~hr^-1)))
```

### 2nd order polynomial?
```{r}
#polynomial ancova
  clean.full.calc$temp_treatment <-as.factor(clean.full.calc$temp_treatment)
  clean.full.calc$experiment <- as.factor (clean.full.calc$experiment)
  calcpoly <- lm(umol.cm2.hr ~ poly(pH_treatment,2) * temp_treatment, data = clean.full.calc)
  #plot(calcpoly)
  anova(calcpoly)

  #with effect for experiment
  calcpolyrando <-lm(umol.cm2.hr ~ poly(pH_treatment,2) * temp_treatment + experiment, data = clean.full.calc)
  anova(calcpolyrando)

  AIC(calcpoly)
  AIC(calcpolyrando)

clean.full.calc <- clean.full.calc %>%
  mutate(model = predict(calcpoly)) #model prediction for plot
```

```{r echo=FALSE}
## try plotting 
ggplot(data = clean.full.calc, aes(x = pH_treatment, y = umol.cm2.hr, group = interaction(pH_treatment, temp_treatment), fill = as.factor(temp_treatment))) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.8, alpha = 0.3) +
  stat_summary(aes(color = as.factor(temp_treatment)), fun.data = mean_se, fun.args = list(mult = 1), 
               geom = "pointrange", size = 0.5) +
  geom_line(aes(y = model, group = temp_treatment, color = as.factor(temp_treatment))) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
       text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y = expression(Calcification~rate~(μmol~CaCO[3]~g^-1~hr^-1)))
```

### Gaussian?
```{r}
#polynomial ancova
  calc_g_reduced <- glm(umol.cm2.hr ~ pH_treatment * temp_treatment, family = "gaussian", data = clean.full.calc)
  #plot(calcpoly)
  anova(calc_g_reduced)

  #with effect for experiment
  calc_g_full <-lm(umol.cm2.hr ~ pH_treatment * temp_treatment + experiment, family = "gaussian", data = clean.full.calc)
  anova(calc_g_full)

  AIC(calc_g_reduced)
  AIC(calc_g_full)

clean.full.calc <- clean.full.calc %>%
  mutate(model = predict(calc_g_reduced)) #model prediction for plot
```

```{r echo=FALSE}
## try plotting 
ggplot(data = clean.full.calc, aes(x = pH_treatment, y = umol.cm2.hr, group = interaction(pH_treatment, temp_treatment), fill = as.factor(temp_treatment))) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.8, alpha = 0.3) +
  stat_summary(aes(color = as.factor(temp_treatment)), fun.data = mean_se, fun.args = list(mult = 1), 
               geom = "pointrange", size = 0.5) +
  geom_line(aes(y = model, group = temp_treatment, color = as.factor(temp_treatment))) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
       text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y = expression(Calcification~rate~(μmol~CaCO[3]~g^-1~hr^-1)))
```

### Model selection
```{r}
AIC(calcpoly)
AIC(calclin_reduced)
AIC(calc_g_reduced)
```

## Normalized to dry shell weight
```{r}
clean.full.calc$umol.cm2.hr<-((clean.full.calc$deltaTA/2)*(1.025)*(clean.full.calc$volume))/((clean.full.calc$dry_shell_weight)*(clean.full.calc$timediff))
```


### Linear?
```{r}
#Linear ancova
  calclin_reduced <- lm(umol.cm2.hr ~ pH_treatment * temp_treatment, data = clean.full.calc)
  #plot(calcpoly)
  anova(calclin_reduced)

  #with with effect for experiment
  calclin_full <-lm(umol.cm2.hr ~ pH_treatment * temp_treatment + experiment, data = clean.full.calc)
  anova(calclin_full)

  AIC(calclin_full)
  AIC(calclin_reduced) #lower

clean.full.calc <- clean.full.calc %>%
  mutate(model = predict(calclin_reduced)) #model prediction for plot
```

```{r echo=FALSE}
ggplot(data = clean.full.calc, aes(x = pH_treatment, y = umol.cm2.hr, group = interaction(pH_treatment, temp_treatment), fill = as.factor(temp_treatment))) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.8, alpha = 0.3) +
  stat_summary(aes(color = as.factor(temp_treatment)), fun.data = mean_se, fun.args = list(mult = 1), 
               geom = "pointrange", size = 0.5) +
  geom_line(aes(y = model, group = temp_treatment, color = as.factor(temp_treatment))) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
       text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y = expression(Calcification~rate~(μmol~CaCO[3]~g^-1~hr^-1)))
```

### 2nd order polynomial?
```{r}
#polynomial ancova
  clean.full.calc$temp_treatment <-as.factor(clean.full.calc$temp_treatment)
  clean.full.calc$experiment <- as.factor (clean.full.calc$experiment)
  calcpoly <- lm(umol.cm2.hr ~ poly(pH_treatment,2) * temp_treatment, data = clean.full.calc)
  #plot(calcpoly)
  anova(calcpoly)

  #with effect for experiment
  calcpolyrando <-lm(umol.cm2.hr ~ poly(pH_treatment,2) * temp_treatment + experiment, data = clean.full.calc)
  anova(calcpolyrando)

  AIC(calcpoly)
  AIC(calcpolyrando)

clean.full.calc <- clean.full.calc %>%
  mutate(model = predict(calcpoly)) #model prediction for plot
```

```{r echo=FALSE}
## try plotting 
ggplot(data = clean.full.calc, aes(x = pH_treatment, y = umol.cm2.hr, group = interaction(pH_treatment, temp_treatment), fill = as.factor(temp_treatment))) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.8, alpha = 0.3) +
  stat_summary(aes(color = as.factor(temp_treatment)), fun.data = mean_se, fun.args = list(mult = 1), 
               geom = "pointrange", size = 0.5) +
  geom_line(aes(y = model, group = temp_treatment, color = as.factor(temp_treatment))) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
       text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y = expression(Calcification~rate~(μmol~CaCO[3]~g^-1~hr^-1)))
```

### Gaussian?
```{r}
#polynomial ancova
  calc_g_reduced <- glm(umol.cm2.hr ~ pH_treatment * temp_treatment, family = "gaussian", data = clean.full.calc)
  #plot(calcpoly)
  anova(calc_g_reduced)

  #with effect for experiment
  calc_g_full <-lm(umol.cm2.hr ~ pH_treatment * temp_treatment + experiment, family = "gaussian", data = clean.full.calc)
  anova(calc_g_full)

  AIC(calc_g_reduced)
  AIC(calc_g_full)

clean.full.calc <- clean.full.calc %>%
  mutate(model = predict(calc_g_reduced)) #model prediction for plot
```

```{r echo=FALSE}
## try plotting 
ggplot(data = clean.full.calc, aes(x = pH_treatment, y = umol.cm2.hr, group = interaction(pH_treatment, temp_treatment), fill = as.factor(temp_treatment))) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.8, alpha = 0.3) +
  stat_summary(aes(color = as.factor(temp_treatment)), fun.data = mean_se, fun.args = list(mult = 1), 
               geom = "pointrange", size = 0.5) +
  geom_line(aes(y = model, group = temp_treatment, color = as.factor(temp_treatment))) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
       text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y = expression(Calcification~rate~(μmol~CaCO[3]~g^-1~hr^-1)))
```

### Model selection
```{r}
AIC(calcpoly)
AIC(calclin_reduced)
AIC(calc_g_reduced)
```